\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[style=authoryear]{biblatex}

\addbibresource{sample.bib}

\newcommand{\mysection}[1]{\noindent\textbf{\underline{#1}}}
\newcommand{\mysubsection}[1]{\noindent\textbf{#1}}

\begin{document}

\begin{center}
    \thispagestyle{empty}
    {\large\textbf{Jerry Lingjie Mei}} \\
    \normalsize
    lm5483@princeton.edu $\mid$
    617-955-7874 $\mid$
    \href{https://www.cs.princeton.edu/~lm5483/}{Website} $\mid$
    \href{https://github.com/JerryLingjieMei/}{Github} $\mid$
    \href{https://scholar.google.com/citations?user=NBGAr-0AAAAJ&hl=en}{Google Scholar} \\
    \hrulefill
\end{center}


\mysection{EDUCATION} \\
\textbf{Princeton University} \hfill Princeton, New Jersey \\
\textit{Ph.D. candidate in Computer Science} \hfill GPA: 3.85/4.0 \hspace{1cm} Sept. 2022 - May 2027 \\
\textbf{Massachusetts Institute of Technology} \hfill Cambridge, Massachusetts \\
\textit{M.Eng. in Computer Science} \hfill GPA: 4.7/5.0 \hspace{1cm} Sept. 2020 - May 2022 \\
\textit{B.Sc. in Computer Science (6-3), and Mathematics (18)} \hfill GPA: 4.9/5.0 \hspace{1cm} Sept. 2017 - May 2020 \\
\textbf{Peking University} \hfill Beijing, China \\
\textit{B.Sc. candidate in Mathematics} \hfill GPA: 3.84/4.00 \hspace{1cm} Sept. 2016 - Jun. 2017 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mysection{RESEARCH INTEREST}

Procedural Generation, 3D vision, Generative AI.


\mysection{PUBLICATIONS}
\begin{itemize}
    \item Jack Nugent, Siyang Wu, Zeyu Ma, Beining Han, Meenal Parakh, Abhishek Joshi, \textbf{Lingjie Mei}, Alexander Raistrick, Xinyuan Li, and Jia Deng.
    \href{https://arxiv.org/abs/2507.00981}{Evaluating Robustness of Monocular Depth Estimation with Procedural Scene Perturbations}.
    \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2025.

    \item Alexander Raistrick*, \textbf{Lingjie Mei*}, Karhan Kayan*, David Yan, Yiming Zuo, Beining Han, Hongyu Wen, Meenal Parakh, Stamatis Alexandropoulos, Lahav Lipson, Zeyu Ma, and Jia Deng.
    \href{https://openaccess.thecvf.com/content/CVPR2024/html/Raistrick_Infinigen_Indoors_Photorealistic_Indoor_Scenes_using_Procedural_Generation_CVPR_2024_paper.html}{Infinigen Indoors: Photorealistic Indoor Scenes using Procedural Generation}.
    \textit{IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 2024.

    \item Shari Liu, Kirsten Lydic, \textbf{Lingjie Mei}, and Rebecca Saxe.
    \href{https://direct.mit.edu/imag/article/doi/10.1162/imag_a_00068/118940}{Violations of physical and psychological expectations in the human adult brain}.
    \textit{Imaging Neuroscience}, 2024; \textit{Proceedings of the 45th Annual Meeting of the Cognitive Science Society (CogSci)}, 2023.

    \item Alexander Raistrick*, Lahav Lipson*, Zeyu Ma*, \textbf{Lingjie Mei*}, Mingzhe Wang, Yiming Zuo, Karhan Kayan, Hongyu Wen, Beining Han, Yihan Wang, Alejandro Newell, Hei Law, Ankit Goyal, Kaiyu Yang, and Jia Deng.
    \href{https://openaccess.thecvf.com/content/CVPR2023/html/Raistrick_Infinite_Photorealistic_Worlds_Using_Procedural_Generation_CVPR_2023_paper.html}{Infinite Photorealistic Worlds Using Procedural Generation}.
    \textit{IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 2023.

    \item \textbf{Lingjie Mei*}, Jiayuan Mao*, Ziqi Wang, Chuang Gan, and Joshua B. Tenenbaum.
    \href{https://openreview.net/forum?id=htWIlvDcY8}{FALCON: Fast Visual Concept Learning by Integrating Images, Linguistic descriptions, and Conceptual Relations}.
    \textit{The Tenth International Conference on Learning Representations (ICLR)}, 2022.

    \item Kevin Smith, \textbf{Lingjie Mei}, Shunyu Yao, Jiajun Wu, Elizabeth S. Spelke, Josh Tenenbaum, and Tomer D. Ullman.
    \href{https://escholarship.org/uc/item/07t8021w}{The fine structure of surprise in intuitive physics: when, why, and how much?}
    \textit{Proceedings of the 42th Annual Meeting of the Cognitive Science Society (CogSci)}, 2020.

    \item Kevin Smith, \textbf{Lingjie Mei*}, Shunyu Yao, Jiajun Wu, Elizabeth S. Spelke, Josh Tenenbaum, and Tomer D. Ullman.
    \href{https://proceedings.neurips.cc/paper/2019/hash/e88f243bf341ded9b4ced444795c3f17-Abstract.html}{Modeling Expectation Violation in Intuitive Physics with Coarse Probabilistic Object Representations}.
    \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2019.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra-Curricular Activities, Leadership, etc.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mysection{SERVICES}
\begin{itemize}[noitemsep, nolistsep, leftmargin=*]
    \item Teaching Assistant/Precepter for MIT 6.036, Princeton COS 324 and COS 423.
    \item Reviewers for NeurIPS 2024, EECV 2024, NeurIPS 2025, ICCV 2025, CVPR 2026.
\end{itemize}


\mysection{OTHER MISC PROJECTS}
\mysubsection{Paper projects}
\begin{itemize}[noitemsep, nolistsep, leftmargin=*]
    \item \href{https://github.com/princeton-vl/infinigen}{princeton-vl/infinigen}: core contributor to Princeton VL's flagship procedural scene generator (6.9k\,$\star$).
    \item \href{https://github.com/JerryLingjieMei/ADEPT-Model-Release}{ADEPT-Model-Release}: model code for the ADEPT intuitive-physics project (NeurIPS 2019).
    \item \href{https://github.com/JerryLingjieMei/ADEPT-Dataset-Release}{ADEPT-Dataset-Release}: dataset generation code for ADEPT.
    \item \href{https://github.com/JerryLingjieMei/FALCON-Release}{FALCON-Release}: PyTorch reference implementation for the FALCON visual concept learner (ICLR 2022).
    \item \href{https://github.com/princeton-vl/cvdpack}{princeton-vl/cvdpack}: contributor to tooling for reorganizing/compressing RGB/Depth/Flow/Normal frame datasets.
 \end{itemize}

\mysubsection{Non-paper projects}
\begin{itemize}[noitemsep, nolistsep, leftmargin=*]
    \item \href{https://github.com/blocher/dailyoffice2019}{blocher/dailyoffice2019}: contributor via pull requests to the Daily Office 2019 website codebase.
    \item \href{https://github.com/JerryLingjieMei/WinogradConvolution}{WinogradConvolution}: Julia + CUDA implementation of Winograd convolution kernels.
    \item \href{https://github.com/JerryLingjieMei/NonlinearPDE}{NonlinearPDE}: multigrid-based iterative solver for nonlinear PDEs.
    \item \href{https://github.com/JerryLingjieMei/BayesianLanguageLearningPython}{BayesianLanguageLearningPython}: compositional language evolution from a Bayesian perspective.
    \item \href{https://github.com/JerryLingjieMei/Contour3D}{Contour3D}: 3D contour reconstruction and visualization experiments.
    \item \href{https://github.com/JerryLingjieMei/FastMultipleMethod}{FastMultipleMethod}: implementation of 1D fast multipole method.
    \item \href{https://github.com/JerryLingjieMei/StarRailCopilot}{StarRailCopilot}: maintained fork for Honkai: Star Rail automation tooling.
    \item \href{https://github.com/JerryLingjieMei/ece475-proj}{ece475-proj}: RISC-V 32I processor with vectorization support.
    \item \href{https://github.com/JerryLingjieMei/Competitive_SIR}{Competitive\_SIR}: simulation of competing rumor dynamics with compartmental models.
    \item \href{https://github.com/JerryLingjieMei/AtariRepresentation}{AtariRepresentation}: experiments on representation generalization in Atari games.
\end{itemize}


\mysection{ACTIVITIES}
\begin{itemize}[noitemsep, nolistsep, leftmargin=*]
    \item Prior to coming to MIT, I won the Gold Medal at the 2016 International Mathematical Olympiad (IMO).
    \item During my years at MIT, I am involved with MIT ATS, MIT Asian dance team, MIT CUCN and MIT Technique. I was also top 25 individual at 2017 Putnam; and won the Boston Dragon Boat Race.
    \item During my years at Princeton, I am involved with Princeton ECP. I was also a memeber of the IEEE-Eta Kappa Nu Honor Society.
\end{itemize}

\end{document}
